---
title: "Assignment B-1"
author: "Hannah Hauch"
output: github_document
---

```{r}
library(datateachr) 
library(tidyverse) 
library(roxygen2)
library(palmerpenguins)
library(testthat)
```
###Exercise 1 & 2: Make and Document a Function 

```{r}
#' @title Create Summary Table from Data Set
#' 
#' @description Creates a summary table for a chosen variable with mean, median, max, min, interquartile range (IQR), and standard deviation grouped by another variable in the data set
#' 
#' @param df: Data frame of choice, Named df as this is an abbreviation of Data Frame
#' @param group_cat: The variable that the summarize function will be grouped by. Named group_cat as this categorical variable will be used in the group_by function. 
#' @param Summary_num: the numerical variable that the summary will be made for. Named summary_num as this is the numerical variable that will be used in the summarize function
#' @param na.rm = True: To drop the missing values from the calculation, it is not hard coded so the user can decided. 
#' @param ... allows for extra augments to be added to augment the functions inside such as mean or median. 
#' @return the function returns a summary table tibble that includes:
#' \itemize {
#' \item group_cat: the categorical variable
#' \item mean: average value per group(s)
#' \item median: median value per group(s)
#' \item max: maximum value per group(s)
#' \item min: minimum value per group(s)
#' \item IQR: interquartile range of the group(s)
#' \item sd: standard deviation for the group(s)}

summary_table <- function(df, group_cat, summary_num, na.rm = TRUE, ...) {
  stopifnot(is.data.frame(df))
  df %>%
  group_by({{group_cat}}) %>%
  summarize(mean = mean({{summary_num}}, na.rm = na.rm),
  median = median({{summary_num}}, na.rm = na.rm),
  max = max({{summary_num}}, na.rm = na.rm),
  min = min({{summary_num}}, na.rm = na.rm),
  IQR = IQR({{summary_num}}, na.rm = na.rm),
  sd = sd({{summary_num}}, na.rm = na.rm))

}
```


### Exercise 3: Examples with Function 
#### Testing with cancer_sample data set
I applied the function to make a summary table on the cancer_sample data set where the categorical variable is the diagnosis and the numerical variable is the texture_mean. I expected that I would get a table that showed the mean, median, max, min, IQR, and sd for texture_mean from benign and metastatic cells. 
```{r}
summarize_texture_table <- summary_table(cancer_sample, diagnosis, texture_mean)

print(summarize_texture_table)
```
#### Testing with penguins data set
I applied the function to make a summary table on the penguins data set where the categorical variable is the island and the numerical variable is the bill length in mm. I expected that I would get a table that showed the mean, median, max, min, IQR, and sd for bill length for penguins on the Biscoe, Dream, and Torgersen islands respectively. 
```{r}
summarize_bill_length_island <- summary_table(penguins, island, bill_length_mm)

print(summarize_bill_length_island)
```

### Exercise 4: Test the Function 

```{r}
test_that("Invalid Aruguments", { #this test_that checks to make sure there are not invalid inputs
  expect_error(summary_table("cancer_sample", diagnosis, texture_mean)) #this checks that one of the inputs isn't a string
  expect_error(summary_table(5,12,3)) #this checks against just numerical input
  expect_error(summary_table(cancer_sample, texture_mean, diagnosis)) #this checks against switching the numerical variable and the categorical variable 
})


test_that('NA handling works', { #this test checks that the NA handling works 
  expect_error(summary_table(summary_table(penguins, island, body_mass_g, na.rm = FALSE))) #If na.rm=FALSE we would expect an error, however it is up to the user to decided if it is TRUE or FALSE
  expect_no_error(summary_table(penguins, island, body_mass_g, na.rm = TRUE)) #no error is expected when na.rm = TRUE
               })

test_that('Output is correct type', {
expect_type(summary_table(penguins, island, body_mass_g), "list")
expect_named(summary_table(penguins, island, body_mass_g), c("island", "mean", "median", "max", "min", "IQR", "sd"))
})



```



